### 2016-11-22 Projects/DelCo_2012/Report/DelCo_2012.tex
update report and door legend CAF

\headerC{
\flushright{
Craig G. Weinschenk $^+$ \\
Daniel Madrzykowski $^*$ \\
Keith M. Stakes $^*$ \\
Joseph M. Willi \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\vspace*{2\baselineskip}
{\em $^+$\small Currently with JENSEN HUGHES, Baltimore MD}
\\
{\em $^*$\small Currently with Underwriters Laboratories Firefighter \\ 
Safety Research Institute, Columbia MD}
}

@@

The series of tests described within this report were conducted at the Delaware County ESTC in Sharon Hill, PA. A burn building and two purpose-built concrete structures are located on the grounds of the ESTC. The burn building was used for the gas cooling experiments, and the purpose-built concrete structures were used for the fire suppression experiments.

@@

The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Adam Barowy (currently with UL), Kelly Opert (currently with UL) and Jay McElroy (retired) from NIST for their contributions in preparing and conducting these experiments. These experiments could not have been conducted without them.

>>>>

\headerC{
\flushright{
Craig G. Weinschenk $^*$ \\
Daniel Madrzykowski $^*$ \\
Keith M. Stakes $^*$ \\
Joseph M. Willi \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\vspace*{2\baselineskip}
{\em $^*$\small Currently with Underwriters Laboratories Firefighter \\ 
Safety Research Institute, Columbia MD}
}

@@

The series of tests described within this report were conducted at the Delaware County ESTC in Sharon Hill, PA. A burn building and two purpose-built concrete structures are located on the grounds of the ESTC. The burn building was used for the gas cooling experiments, and the purpose-built concrete structures were used for the fire suppression experiments. Figure~\ref{fig:Door_Status_Legend} provides the key for determining the status of open or closed doors in the facility schematics.

\begin{figure}[!ht]
	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Door_Legend}
	\caption{Door Status Legend}
	\label{fig:Door_Status_Legend}
\end{figure}

@@

The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Adam Barowy (currently with UL), Kelly Opert (currently with UL) and Jay McElroy (retired) from NIST for their contributions in preparing and conducting these experiments. These experiments could not have been conducted without them.
